---
title: "RFE_implementation_new_data_in_R"
author: "Rajnish Kumar"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Following optimal set up of features were discovered from RFE: > op_features_rfe
 [1] "crp"                       "Age"                       "absolute_monocyte"         "rbc_count"                 "absolute_monocyte_dpi_2"  
 [6] "absolute_lymphocyte"       "absolute_monocyte_dpi_0"   "crp_dpi_2"                 "crp_dpi_1"                 "absolute_monocyte_dpi_1"  
[11] "rbc_count_dpi_1"           "crp_dpi_0"                 "mpv_dpi_0"                 "mch_dpi_0"                 "absolute_lymphocyte_dpi_2"
[16] "rbc_count_dpi_2" 

Here we are exploring these features through visualization of the dataset. 

From Rashmi: Do absolute_neutrophyle and abs_neutrophyle/abs_lymphocyte and Lymphocyte. 


```{r}
# Import libraries
library(readxl)
library(dplyr)
library(tidyr)
library(randomForest)
library(caret)
library(stringr)
library(e1071) # For SVM
library(MLeval)
```

## Including Plots

You can also embed plots, for example:

```{r}
# Read Excel files
# df_CBC_umich <- read_excel('C:\\Users\\rajnishk\\Dropbox (University of Michigan)\\2023-09-25 CBC CART for Benjie and Rajnish from Mary\\data folder 4-4-2024\\cleaned_data_from_Rashmi\\Umich_data_with_demography.xlsx')

# Get the current working directory 
current_dir <- getwd()

# Set the full file path
data_path <- file.path(current_dir, "data_used", "Umich_data_with_demography.xlsx")

# Read the CSV file
df_CBC_umich <- read_excel(data_path)


# df_CBC_JH <- read_excel('C:\\Users\\rajnishk\\Dropbox (University of Michigan)\\2023-09-25 CBC CART for Benjie and Rajnish from Mary\\data folder 4-4-2024\\Test_data_JHU\\04-11-2024 JHMI data with changed names from JHMI Compiled CBC, No ALL, CRP_LOD_0.xlsx')
data_path <- file.path(current_dir, "data_used", "04-11-2024 JHMI data.xlsx")
# Read the CSV file
df_CBC_JH <- read_excel(data_path)


# Assign columns for analysis
columns_for_analysis <- c('studyid', 'dpi', 'wbc_count', 'hgb', 'hct', 'plt', 'rbc_count', 'mcv',
                          'mch', 'mchc', 'rdw', 'mpv', 'absolute_neutrophil',
                          'absolute_lymphocyte', 'absolute_monocyte', 'crp', 'ferritin', 
                          'clinician_defined_crs_grade', 'NT_incidence', 'Age', 'Sex')
```



```{r}
a <- 0
b <- 10
```



```{r}
# Selecting relevant columns for analysis
df_umich <- df_CBC_umich %>% select(all_of(columns_for_analysis))
df_JH <- df_CBC_JH %>% select(all_of(columns_for_analysis))
df_JH <-na.omit(df_JH)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
# Converting 'NT_incidence' to integer
df_JH$NT_incidence <- as.integer(df_JH$NT_incidence)
df_JH$Sex <- factor(df_JH$Sex, levels = c("Male", "Female"))
```


```{r}
# Stripping white space from character columns in df_umich
# character_columns <- df_umich %>% 
#   select_if(is.character) %>% 
#   names()
# 
# df_umich[character_columns] <- lapply(df_umich[character_columns], trimws)
```



```{r}
# Columns to convert (if they are not already numeric, otherwise this step can be skipped)
cols_to_convert <- c('wbc_count', 'hgb', 'hct', 'plt', 'rbc_count', 'mcv', 'mch', 
                     'mchc', 'rdw', 'mpv', 'absolute_neutrophil', 'absolute_lymphocyte',
                     'absolute_monocyte', 'crp')

df_umich <- df_umich %>%
  mutate(across(all_of(cols_to_convert), ~as.numeric(str_trim(.))))

df_umich$Sex <- factor(df_umich$Sex, levels = c("Male", "Female"))

df_umich$NT_incidence <- factor(df_umich$NT_incidence, levels = unique(df_umich$NT_incidence))
df_JH$NT_incidence <- factor(df_JH$NT_incidence, levels = unique(df_JH$NT_incidence))
```




```{r}
# Convert columns to numeric
# for (col in cols_to_convert) {
#   df_umich[[col]] <- as.numeric(df_umich[[col]])
#   # If there are any non-convertible strings, they will be turned into NA
# }

# Map 'Sex' values from Male/Female to 0/1
# sex_mapping <- c(Male = 0, Female = 1)
# df_umich$Sex <- as.integer(factor(df_umich$Sex, levels = names(sex_mapping), labels = sex_mapping))
# df_JH$Sex <- as.integer(factor(df_JH$Sex, levels = names(sex_mapping), labels = sex_mapping))

# Subset data frames for day 0 of relevant dataset
#df_umich_dpi_0 <- subset(df_umich, dpi == 0)
#df_JH_dpi_0 <- subset(df_JH, dpi == 0)

filtered_df_umich_a_to_b <- df_umich %>% filter(dpi >= a & dpi <= b)
filtered_df_JH_a_to_b <- df_JH %>% filter(dpi >= a & dpi <= b)

# Printing the number of measurements in day 0 datasets, using the sprintf function for string formatting
cat(sprintf("no of measurements in filtered_df_umich_a_to_b is %s\n", nrow(filtered_df_umich_a_to_b)))
cat(sprintf("no of measurements in filtered_df_JH_a_to_b is %s\n", nrow(filtered_df_JH_a_to_b)))


```



```{r}

# Drop rows with NAs in specific columns. # We might have to drop NAs for all of the cases, because it might not be same variables that will NAs when you try different combinations of dpi's. 

selected_cols <- c('crp', 'ferritin', 'absolute_neutrophil', 'absolute_lymphocyte', 'absolute_monocyte')
filtered_df_umich_a_to_b <- filtered_df_umich_a_to_b %>%
  filter(complete.cases(select(., all_of(selected_cols))))

# Create a vector of features to be standardized
norm_list <- c('wbc_count', 'absolute_neutrophil', 'absolute_lymphocyte', 'absolute_monocyte', 
               'clinician_defined_crs_grade', 'hgb', 'hct', 'plt', 'rbc_count', 'mcv', 
               'mch', 'mchc', 'rdw', 'mpv', 'Age', 'crp', 'ferritin')

# Standardize the data (Z-score normalization)
filtered_df_umich_a_to_b_norm <- filtered_df_umich_a_to_b

# Calculate mean and standard deviation for each column and then standardize
filtered_df_umich_a_to_b_norm[norm_list] <- scale(filtered_df_umich_a_to_b_norm[norm_list])              # This is not for standardization being done based on JH dataset. 


features_list <- c('wbc_count', 'absolute_neutrophil', 'absolute_lymphocyte', 'absolute_monocyte',
                   'clinician_defined_crs_grade', 'hgb', 'hct', 'plt', 'rbc_count', 'mcv',
                   'mch', 'mchc', 'rdw', 'mpv', 'Sex', 'Age', 'crp', 'ferritin')
```



```{r}
# library(dplyr)
# 
# # Check for participants with both NT_incidence values
# participants_with_both <- df_umich %>%
#   group_by(studyid) %>%
#   summarize(unique_NT_incidence = n_distinct(NT_incidence)) %>%
#   filter(unique_NT_incidence > 1)
# 
# # Display the results
# print(participants_with_both)
# 
# # Check if any participants have both values
# if (nrow(participants_with_both) > 0) {
#   cat("The following participants have both 0 and 1 values for NT_incidence:\n")
#   print(participants_with_both$studyid)
# } else {
#   cat("No participants have both 0 and 1 values for NT_incidence.\n")
# }
# 
# # Count how many participants have both values
# cat("\nNumber of participants with both values:", nrow(participants_with_both))
```



```{r}
# Select a subset of study IDs (e.g., first 10)
subset_ids <- unique(df_umich$studyid)

ggplot(df_umich %>% filter(studyid %in% subset_ids), 
       aes(x = dpi, y = absolute_monocyte, color = studyid, group = studyid)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Absolute Monocyte Count Over Time (Subset of Participants)",
       x = "Days Post Infusion (DPI)",
       y = "Absolute Monocyte Count",
       color = "Study ID")
```

```{r}
# ggplot(df_umich %>% filter(studyid %in% subset_ids), 
#        aes(x = dpi, y = absolute_monocyte)) +
#   geom_line() +
#   facet_wrap(~studyid, scales = "free_y") +
#   theme_minimal() +
#   labs(title = "Changes in Absolute Monocyte Count Over Time",
#        x = "Days Post Infusion (DPI)",
#        y = "Absolute Monocyte Count")
subset_ids <- unique(df_umich$studyid)[1:10]
ggplot(df_umich %>% filter(studyid %in% subset_ids), 
       aes(x = dpi, y = absolute_monocyte)) +
  geom_line() +
  # facet_wrap(~studyid, scales = "free_y") +
  theme_minimal() +
  labs(title = "Changes in Absolute Monocyte Count Over Time",
       x = "Days Post Infusion (DPI)",
       y = "Absolute Monocyte Count")
```

```{r}
ggplot(df_umich, aes(x = dpi, y = absolute_monocyte)) +
  stat_summary(fun = mean, geom = "line", color = "blue") +
  stat_summary(fun.data = mean_cl_normal, geom = "ribbon", alpha = 0.3) +
  theme_minimal() +
  labs(title = "Average Change in Absolute Monocyte Count Over Time",
       x = "Days Post Infusion (DPI)",
       y = "Average Absolute Monocyte Count")
``` 



```{r}
# ggplot(df_umich, aes(x = dpi, y = absolute_monocyte, group = studyid)) +
#   geom_line(aes(color = factor(NT_incidence)), alpha = 0.3) +
#   stat_summary(aes(group = 1), fun = mean, geom = "line", color = "black", size = 1.5) +
#   facet_wrap(~NT_incidence, labeller = labeller(NT_incidence = c("0" = "NT Incidence = 0", "1" = "NT Incidence = 1"))) +
#   scale_color_manual(values = c("0" = "blue", "1" = "red")) +
#   theme_minimal() +
#   labs(title = "Change in Absolute Monocyte Count (Day 0-3)",
#        x = "Days Post Infusion",
#        y = "Absolute Monocyte Count") +
#   scale_x_continuous(breaks = 0:3) +
#   theme(legend.position = "none")

library(ggplot2)
library(dplyr)

ggplot(df_umich, aes(x = dpi, y = absolute_monocyte, color = factor(NT_incidence), 
                     fill = factor(NT_incidence))) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "ribbon", alpha = 0.3) +
  facet_wrap(~ NT_incidence, ncol = 2, 
             labeller = labeller(NT_incidence = c("0" = "NT Incidence = 0", 
                                                  "1" = "NT Incidence = 1"))) +
  scale_color_manual(values = c("0" = "blue", "1" = "red")) +
  scale_fill_manual(values = c("0" = "lightblue", "1" = "pink")) +
  theme_minimal() +
  labs(title = "Average Change in Absolute Monocyte Count Over Time",
       x = "Days Post Infusion (DPI)",
       y = "Average Absolute Monocyte Count") +
  theme(strip.background = element_rect(fill = "lightgray"),
        strip.text = element_text(size = 12, face = "bold"),
        legend.position = "none") 

```




```{r}
library(ggplot2)
library(dplyr)

df_filtered <- df_umich %>%
  filter(dpi >= 0 & dpi <= 3)

ggplot(df_filtered, aes(x = dpi, y = absolute_monocyte, group = studyid, color = factor(NT_incidence))) +
  geom_line(alpha = 0.5) +
  scale_color_manual(values = c("0" = "blue", "1" = "red")) +
  theme_minimal() +
  labs(title = "Change in Absolute Monocyte Count (Day 0-3)",
       x = "Days Post Infusion",
       y = "Absolute Monocyte Count",
       color = "NT Incidence") +
  scale_x_continuous(breaks = 0:3)
```




```{r}
ggplot(df_filtered, aes(x = dpi, y = absolute_monocyte, group = studyid)) +
  geom_line(aes(color = factor(NT_incidence)), alpha = 0.3) +
  stat_summary(aes(group = 1), fun = mean, geom = "line", color = "black", size = 1.5) +
  facet_wrap(~NT_incidence, labeller = labeller(NT_incidence = c("0" = "NT Incidence = 0", "1" = "NT Incidence = 1"))) +
  scale_color_manual(values = c("0" = "blue", "1" = "red")) +
  theme_minimal() +
  labs(title = "Change in Absolute Monocyte Count (Day 0-3)",
       x = "Days Post Infusion",
       y = "Absolute Monocyte Count") +
  scale_x_continuous(breaks = 0:3) +
  theme(legend.position = "none")
```



```{r}
ggplot(df_filtered, aes(x = factor(dpi), y = absolute_monocyte, fill = factor(NT_incidence))) +
  geom_boxplot() +
  scale_fill_manual(values = c("0" = "skyblue", "1" = "salmon")) +
  theme_minimal() +
  labs(title = "Distribution of Absolute Monocyte Count by NT Incidence (Day 0-3)",
       x = "Days Post Infusion",
       y = "Absolute Monocyte Count",
       fill = "NT Incidence")
```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)

df_change <- df_umich %>%
  filter(dpi >= 0 & dpi <= 3) %>%
  group_by(studyid) %>%
  mutate(
    baseline_monocyte = first(absolute_monocyte),
    monocyte_change = absolute_monocyte - baseline_monocyte,
    NT_incidence = factor(NT_incidence)
  ) %>%
  ungroup()
```



```{r}
ggplot(df_change, aes(x = factor(dpi), y = monocyte_change, color = NT_incidence)) +
  # geom_boxplot(outlier.shape = NA) +
  geom_boxplot() +
  geom_jitter(width = 0.4, alpha = 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  scale_color_manual(values = c("0" = "blue", "1" = "red")) +
  theme_minimal() +
  labs(
    title = "Change in Absolute Monocyte Count Relative to Day 0",
    x = "Days Post Infusion",
    y = "Change in Absolute Monocyte Count",
    color = "NT Incidence"
  ) +
  theme(legend.position = "bottom")
```

```{r}
ggplot(df_change, aes(x = dpi, y = monocyte_change, group = studyid, color = NT_incidence)) +
  geom_line(alpha = 0.3) +
  geom_point(alpha = 0.5) +
  stat_summary(aes(group = NT_incidence), fun = mean, geom = "line", size = 1.5) +
  scale_color_manual(values = c("0" = "blue", "1" = "red")) +
  theme_minimal() +
  labs(
    title = "Change in Absolute Monocyte Count Relative to Day 0",
    x = "Days Post Infusion",
    y = "Change in Absolute Monocyte Count",
    color = "NT Incidence"
  ) +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = 0:3)

# df_change$monocyte_change <- as.numeric(as.character(df_change$monocyte_change))
# print(unique(round(df_change$monocyte_change, 5)))
```

```{r}
ggplot(df_change, aes(x = dpi, y = monocyte_change, group = studyid, color = NT_incidence)) +
  geom_line(alpha = 0.3) +
  geom_point(alpha = 0.5) +
  stat_summary(aes(group = 1), fun = mean, geom = "line", size = 1.5, color = "black") +
  facet_wrap(~NT_incidence, ncol = 2, labeller = labeller(NT_incidence = c("0" = "NT Incidence = 0", "1" = "NT Incidence = 1"))) +
  scale_color_manual(values = c("0" = "blue", "1" = "red")) +
  theme_minimal() +
  labs(
    title = "Change in Absolute Monocyte Count Relative to Day 0",
    x = "Days Post Infusion",
    y = "Change in Absolute Monocyte Count"
  ) +
  theme(legend.position = "none") +
  scale_x_continuous(breaks = 0:3)
```
```{r}
df_umich <- df_umich %>% filter(dpi >= a & dpi <= b)
```



```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)

# Assuming df_umich is already loaded in your environment

# Create the plot
ggplot(df_umich, aes(x = dpi, y = rbc_count, color = NT_incidence, group = NT_incidence)) +
  geom_line() +
  geom_point() +
  labs(title = "RBC Count Across Days Post Infusion",
       x = "Days Post Infusion (dpi)",
       y = "RBC Count") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_color_manual(values = c("blue", "red"), labels = c("No NT", "NT"))

```
```{r}
ggplot(df_umich, aes(x = dpi, y = rbc_count, color = NT_incidence, fill = NT_incidence)) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "ribbon", alpha = 0.3, conf.int = 0.95, color = NA) +
  labs(title = "RBC Count Across Days Post Infusion",
       x = "Days Post Infusion (dpi)",
       y = "RBC Count") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_color_manual(values = c("blue", "red"), labels = c("No NT", "NT")) +
  scale_fill_manual(values = c("blue", "red"), labels = c("No NT", "NT"))
```











```{r}
ggplot(df_umich, aes(x = dpi, y = crp, color = NT_incidence, fill = NT_incidence)) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "ribbon", alpha = 0.3, color = NA) +
  labs(title = "crp Count Across Days Post Infusion",
       x = "Days Post Infusion (dpi)",
       y = "crp") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_color_manual(values = c("blue", "red"), labels = c("No NT", "NT")) +
  scale_fill_manual(values = c("blue", "red"), labels = c("No NT", "NT"))
```


```{r}
ggplot(df_umich, aes(x = dpi, y = absolute_lymphocyte, color = NT_incidence, fill = NT_incidence)) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "ribbon", alpha = 0.3, color = NA) +
  labs(title = "absolute_lymphocyte Across Days Post Infusion",
       x = "Days Post Infusion (dpi)",
       y = "absolute_lymphocyte") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_color_manual(values = c("blue", "red"), labels = c("No NT", "NT")) +
  scale_fill_manual(values = c("blue", "red"), labels = c("No NT", "NT"))

```



```{r}
ggplot(df_umich, aes(x = dpi, y = mpv, color = NT_incidence, fill = NT_incidence)) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "ribbon", alpha = 0.3, color = NA) +
  labs(title = "mpv Across Days Post Infusion",
       x = "Days Post Infusion (dpi)",
       y = "mpv") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_color_manual(values = c("blue", "red"), labels = c("No NT", "NT")) +
  scale_fill_manual(values = c("blue", "red"), labels = c("No NT", "NT"))
```




```{r}
# Reshape the data
df_long <- df_umich %>%
  select(dpi, NT_incidence, absolute_neutrophil, absolute_lymphocyte) %>%
  pivot_longer(cols = c(absolute_neutrophil, absolute_lymphocyte), 
               names_to = "cell_type", 
               values_to = "count")

# Create the plot using ggplot2
ggplot(df_long, aes(x = dpi, y = count, color = NT_incidence, linetype = cell_type, fill = NT_incidence)) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "ribbon", alpha = 0.3, color = NA) +
  labs(title = "Absolute Neutrophil and Lymphocyte Counts Across Days Post Infusion",
       x = "Days Post Infusion (dpi)",
       y = "Cell Count",
       linetype = "Cell Type") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_color_manual(values = c("blue", "red"), labels = c("No NT", "NT")) +
  scale_fill_manual(values = c("blue", "red"), labels = c("No NT", "NT"))
```



```{r}
# Calculate the ratio
df_umich <- df_umich %>%
  mutate(neutrophil_lymphocyte_ratio = absolute_neutrophil / absolute_lymphocyte)
  # mutate(neutrophil_lymphocyte_ratio =  absolute_lymphocyte / absolute_neutrophil )

# Create the plot using ggplot2
ggplot(df_umich, aes(x = dpi, y = neutrophil_lymphocyte_ratio, color = NT_incidence, fill = NT_incidence)) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "ribbon", alpha = 0.3, color = NA) +
  labs(title = "Neutrophil/Lymphocyte Ratio Across Days Post Infusion",
       x = "Days Post Infusion (dpi)",
       y = "Neutrophil/Lymphocyte Ratio") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_color_manual(values = c("blue", "red"), labels = c("No NT", "NT")) +
  scale_fill_manual(values = c("blue", "red"), labels = c("No NT", "NT"))
```



```{r}
df_umich <- df_umich %>%
  mutate(product_crp_monocyte_rbc = crp * absolute_monocyte * rbc_count)

# Create the plot using ggplot2
ggplot(df_umich, aes(x = dpi, y = product_crp_monocyte_rbc, color = NT_incidence, fill = NT_incidence)) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "ribbon", alpha = 0.3, color = NA) +
  labs(title = "Product of CRP, Absolute Monocyte, and RBC Count Across Days Post Infusion",
       x = "Days Post Infusion (dpi)",
       y = "Product of CRP, Absolute Monocyte, and RBC Count") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_color_manual(values = c("blue", "red"), labels = c("No NT", "NT")) +
  scale_fill_manual(values = c("blue", "red"), labels = c("No NT", "NT"))
```



```{r}
df_umich <- df_umich %>%
  mutate(product_monocyte_rbc = absolute_monocyte * rbc_count)

# Create the plot using ggplot2
ggplot(df_umich, aes(x = dpi, y = product_monocyte_rbc, color = NT_incidence, fill = NT_incidence)) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "ribbon", alpha = 0.3, color = NA) +
  labs(title = "Product of  Absolute Monocyte, and RBC Count Across Days Post Infusion",
       x = "Days Post Infusion (dpi)",
       y = "Product of Absolute Monocyte, and RBC Count") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_color_manual(values = c("blue", "red"), labels = c("No NT", "NT")) +
  scale_fill_manual(values = c("blue", "red"), labels = c("No NT", "NT"))
```



```{r}
df_umich <- df_umich %>%
  mutate(product_crp_rbc = crp * rbc_count)

# Create the plot using ggplot2
ggplot(df_umich, aes(x = dpi, y = product_crp_rbc, color = NT_incidence, fill = NT_incidence)) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "ribbon", alpha = 0.3, color = NA) +
  labs(title = "Product of CRP,  and RBC Count Across Days Post Infusion",
       x = "Days Post Infusion (dpi)",
       y = "Product of CRP,  and RBC Count") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_color_manual(values = c("blue", "red"), labels = c("No NT", "NT")) +
  scale_fill_manual(values = c("blue", "red"), labels = c("No NT", "NT"))
```

```{r}
df_umich <- df_umich %>%
  mutate(ratio_crp_rbc = crp / rbc_count)
   # mutate(ratio_crp_rbc = crp / rbc_count)

# Create the plot using ggplot2
ggplot(df_umich, aes(x = dpi, y = ratio_crp_rbc, color = NT_incidence, fill = NT_incidence)) +
  stat_summary(fun = mean, geom = "line", size = 1) +
  stat_summary(fun.data = mean_cl_normal, geom = "ribbon", alpha = 0.3, color = NA) +
  labs(title = "Ratio of CRP,  and RBC Count Across Days Post Infusion",
       x = "Days Post Infusion (dpi)",
       y = "Ratio of CRP,  and RBC Count") +
  theme_minimal() +
  theme(legend.title = element_blank()) +
  scale_color_manual(values = c("blue", "red"), labels = c("No NT", "NT")) +
  scale_fill_manual(values = c("blue", "red"), labels = c("No NT", "NT"))
```

